### 2022-06-13 paper.tex
moved panel letters

Lukas P.~M. Kremer\textsuperscript{1,2,*}, Leonie Küchenhoff\textsuperscript{1,2}, Santiago Cerrizuela\textsuperscript{2}, ..., Ana Martin-Villalba\textsuperscript{2}, Simon Anders\textsuperscript{1,*}\\[1ex]
{\footnotesize \textsuperscript{1} BioQuant Centre, University of Heidelberg, Heidelberg, Germany\\[-.5ex]
\textsuperscript{2} Molecular Neurobiology Dept., German Cancer Research Center (DKFZ), Heidelberg, Germany}
\vspace{1.5ex}

@@

@@

%\begin{figure}
%   \framebox[\columnwidth]{
%       \begin{minipage}[c][3.5cm]{\columnwidth}
%           \centering Figure
%       \end{minipage}
%   }
%   \caption{\small UMAP representations of the single-cell bisulfite data of XXX et al., calculated \textbf{(A)} using conventional preprocessing and \textbf{(B)} using the approach described here.}
%   \label{umaps}
%\end{figure}

@@

%As an example, we will use in this paper data from \citet{luo2017single}, who performed scBS on 16 neuronal subtypes of the mouse frontal cortex, and analysed their data in the manner just described.
%Figure \ref{umaps}A shows a UMAP plot, derived from our re-analysis of the data, using a tiling of the genome into windows of size 100~kb. As one can see, the approach is suitable to see clear structure in the data, observe ...

@@

\begin{figure*}
    A\\
    \begin{center}
        \includegraphics[width=0.7\textwidth]{figures/Fig_residuals_A.png}\\
    \end{center}
    B\\
    \begin{center}
        \includegraphics[width=0.7\textwidth]{figures/Fig_residuals_B.png}
    \end{center}
\caption{\small \textbf{Effect of read position:} \textbf{(A)} Depicted is a genomic interval along a chromosome, for which DNA methylation is to be quantified. Two cells cover differing parts of the interval with one read each. If one simply counts for each cell which fraction of the covered CpG sites are methylated, one obtains very different values for the two cells. \textbf{(B)} By averaging each CpG site's methylation over all cells and subsequent smoothing, the thick black ``average methylation curve'' is obtained. To quantify the methylation of cell 1 from (A) relative to this average over all cells, we propose to use the cell's residuals to the smoothed curve (lengths of the vertical red lines) and take their average, counting residuals of methylated CpGs positive and residuals of unmethylated CpGs negative.}
\label{fig:smoothres}
\end{figure*}

@@

We then run a kernel smoother over these per-position averages to obtain the smoothed averages $\tilde x_i$. Specifically, we use

\[ \tilde x_i = \frac{\sum_{i'} \overline x_{i'}\, k_h(d_{ii'})}{\sum_{i'} k_h(d_{ii'})},\]
i.e., $\tilde x_i$ is the weighted average over the per-position averages $\overline{x}_{i'}$, taken over the CpG sites $i'$ in the neighborhood of $i$, and weighted using a smoothing kernel $k_h$ with bandwidth $h$. Here, $d_{ii'}$ is the distance between CpG positions $i$ and $i'$, measured in base pairs, $h$ is the smoothing bandwidth in base pairs (by default, $h=1000$), and $k_h$ is the tricube kernel,

>>>>

Lukas P.~M. Kremer\textsuperscript{1,2,*}, Leonie Küchenhoff\textsuperscript{1,2}, Santiago Cerrizuela\textsuperscript{2}, \todo{...}, Ana Martin-Villalba\textsuperscript{2}, Simon Anders\textsuperscript{1,*}\\[1ex]
{\footnotesize \textsuperscript{1} BioQuant Centre, University of Heidelberg, Heidelberg, Germany\\[-.5ex]
\textsuperscript{2} Molecular Neurobiology Dept., German Cancer Research Center (DKFZ), Heidelberg, Germany}
\vspace{1.5ex}

@@

\begin{figure*}
	\hspace{2.5cm}A\\[-7ex]
	\begin{center}
		\includegraphics[width=0.7\textwidth]{figures/Fig_residuals_A.png}\\
	\end{center}
	\hspace{2.5cm}B\\[-3ex]
	\begin{center}
		\includegraphics[width=0.7\textwidth]{figures/Fig_residuals_B.png}
	\end{center}
	\caption{\small \textbf{Effect of read position:} \textbf{(A)} Depicted is a genomic interval along a chromosome, for which DNA methylation is to be quantified. Two cells cover differing parts of the interval with one read each. If one simply counts for each cell which fraction of the covered CpG sites are methylated, one obtains very different values for the two cells. \textbf{(B)} By averaging each CpG site's methylation over all cells and subsequent smoothing, the thick black ``average methylation curve'' is obtained. To quantify the methylation of cell 1 from (A) relative to this average over all cells, we propose to use the cell's residuals to the smoothed curve (lengths of the vertical red lines) and take their average, counting residuals of methylated CpGs positive and residuals of unmethylated CpGs negative.}
	\label{fig:smoothres}
\end{figure*}

@@

@@

@@

@@

We then run a kernel smoother over these per-position averages to obtain the smoothed averages $\tilde x_i$. Specifically, we use
\[ \tilde x_i = \frac{\sum_{i'} \overline x_{i'}\, k_h(d_{ii'})}{\sum_{i'} k_h(d_{ii'})},\]
i.e., $\tilde x_i$ is the weighted average over the per-position averages $\overline{x}_{i'}$, taken over the CpG sites $i'$ in the neighborhood of $i$, and weighted using a smoothing kernel $k_h$ with bandwidth $h$. Here, $d_{ii'}$ is the distance between CpG positions $i$ and $i'$, measured in base pairs, $h$ is the smoothing bandwidth in base pairs (by default, $h=1000$), and $k_h$ is the tricube kernel,
